### 2021-04-16 README.Rmd
trying to get the vignette to work in the build

- For more information about SHAP values in general, you can visit the [SHAP github page](https://github.com/slundberg/shap)
- If you use `{mshap}`, please cite [this article](https://google.com)

>>>>

- For more information about SHAP values in general, you can visit the [SHAP github page](https://github.com/slundberg/shap)
- If you use `{mshap}`, please cite [this article](https://google.com/)
